Effects of sexual selection on non-sexual fitness components: a meta-analysis

### 2018-05-15 meta_analysis_sexual_selection_pop_fitness.Rmd
brms add

```{r}
anova(model.complete2, L=c(1, 0, 0, -1, 0, 0)) 
```

>>>>

```{r}
anova(model.complete2, L=c(1, 0, 0, -1, 0, 0)) 
```
__________________________________

###Bayesian models using _brms_ package

We can run a bayesian model using the brms package. The model has the same moderators as the REML approach used above. 
```{r}
library(rstan) #Note that installation requires some effort
library(brms) 
library(backports) #seems to be a dependency

#Use brm to create a model similar to the one used in the REML approach. 
meta.brms <- brm(g | se(sqrt(var.g), sigma = TRUE) ~ 1 + Sex * Environment 
                + (1|Study.ID) 
                + (1|Outcome),
                control = list(adapt_delta = 0.95),
                data = restricted.data)

summary(meta.brms)
```

Plot summart of model
```{r}
plot(meta.brms)
```

Obtain marginal effects plots
```{r}
marginal_effects(meta.brms)
```
